Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
slides

::: {.fragment}
-   **Salient ranks**: output ranks of the competition you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
=======
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank (*k*=1)
    -   Efficacy: 1 through $n$ are salient ranks (*k*=n)
:::

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different competition structures recover the true ranking

>>>>

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank (*k*=1)
    -   Efficacy: 1 through $n$ are salient ranks (*k*=n)
:::

@@
